\documentclass[margin,line]{res}

\usepackage{version}
\usepackage{versions}
\usepackage{url}
\usepackage{booktabs}
\usepackage{enumitem}
\usepackage[usenames,dvipsnames]{color}

\setlength{\pdfpagewidth}{\paperwidth}
\setlength{\pdfpageheight}{\paperheight} 

\widowpenalties 1 10000
\raggedbottom

\oddsidemargin -.5in
\evensidemargin -.5in
%\topmargin-2cm
\textwidth=6.0in
\textheight23.5cm
\itemsep=0in
\parsep=0in

\newenvironment{list1}{
  \begin{list}{\ding{113}}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.17in}}}{\end{list}}
\newenvironment{list2}{
  \begin{list}{$\bullet$}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.2in}}}{\end{list}}

%\newcommand{\pubunder}[1]{\underline{#1}}
\newcommand{\pubunder}[1]{#1}

%-------------------------------------------------------------------------------
% this makes list spacing much better.
%-------------------------------------------------------------------------------
\newenvironment{tightenumerate}{
\begin{enumerate}
  \setlength{\itemsep}{1pt}
  \setlength{\parskip}{0pt}
  \setlength{\parsep}{0pt}
}{\end{enumerate}
}

%-------------------------------------------------------------------------------
% this makes list spacing much better.
%-------------------------------------------------------------------------------
\newenvironment{tightitemize0}{
\begin{itemize}[label={}, leftmargin=0mm]
  \setlength{\itemsep}{1pt}
  \setlength{\parskip}{0pt}
  \setlength{\parsep}{0pt}
}{\end{itemize}
}

\newenvironment{tightitemize1}{
\begin{itemize}[label={}, leftmargin=5mm]
  \setlength{\itemsep}{1pt}
  \setlength{\parskip}{0pt}
  \setlength{\parsep}{0pt}
}{\end{itemize}
}

\includeversion{LONG} 
%\excludeversion{LONG} 

%\includeversion{IMPACT}
\excludeversion{IMPACT}

\includeversion{PENDING}
%\excludeversion{PENDING}

\begin{document}

\name{\Large{John Edwards, Ph.D.} \vspace*{.1in}}

\begin{resume}
\section{\sc Contact Information}
\vspace{.05in}
%\begin{tabular}{@{}p{3in}p{3in}}
%\begin{tabular}{@{}p{3.7in}p{3in}}
%Center for Extreme Data Management and Visualization & \\
%Scientific Computing and Imaging Institute   &  \\%801.585.3911 (office)  \\ 
%University of Utah      &  (385) 207-8331 \\
%WEB 4660          &  jedwards@sci.utah.edu \\
%Salt Lake City, UT 84112                &  http://sci.utah.edu/$\sim$jedwards
%\end{tabular}

%\begin{tabular}{@{}p{3.7in}p{3in}}
%Center for Extreme Data Management and Visualization & (385) 207-8331 \\
%Scientific Computing and Imaging Institute   & jedwards@sci.utah.edu \\
%University of Utah      &  http://sci.utah.edu/$\sim$jedwards \\
%WEB 4660          &  \\
%Salt Lake City, UT 84112                & 
%\end{tabular}

\begin{tabular}{@{}p{3.3in}p{3in}}
Department of Computer Science & (435) 797-0246 \\
Utah State University   & john.edwards@usu.edu \\
%MAIN 401D      &  www2.cose.isu.edu/$\sim$edwajohn \\
%MAIN 401D      &  cs.usu.edu/people/faculty/edwards-john \\
MAIN 401D      &  edwardsjohnmartin.github.io \\
Logan, UT 84322          &
\end{tabular}

%\section{\sc Research Interests}
\section{\sc Research}

Data visualization, CS education, data science

\section{\sc Education}

%\textbf{Ph.D.} Computer Science, The University of Texas, 2013\\
%\textbf{M.S.} Computer Science, Brigham Young University, 2004\\
%\textbf{B.S.} Computer Science, Utah State University, 1998\\
Ph.D. Computer Science, The University of Texas, 2013\\
M.S. Computer Science, Brigham Young University, 2004\\
B.S. Computer Science, Utah State University, 1998\\

\section{\sc Professional experience}

Assistant professor, Utah State University, 2018-current\\
Assistant professor, Idaho State University, 2015-2018\\
Post-doctoral fellow, Scientific Computing and Imaging
Institute, University of Utah, 2013-2015\\
Visiting scholar, University of Hong Kong, 2012\\
Assistant instructor (during PhD studies), The University of Texas, 2010-2013\\
Robotics and visualization research engineer, Autonomous Solutions, Inc., 2008-2009\\
Research and development engineer, ProLogic, Inc., 2005-2008 \\
Software engineer, Rigaku, Inc., 1999-2005 \\

%\section{\sc Peer-reviewed publications}
%\vspace{1.2cm}
\section{\sc Journal publications}

Lloyd Griffel$^*$, Donna Delparte, and John Edwards. Using Support Vector Machines classification to differentiate spectral signatures of potato plants infected with Potato Virus Y. \textit{Computers and electronics in agriculture}, 153, 318-324. 2018.
% CiteScore impact factor: 2.78

DeWayne Derryberry, Ken Aho, \pubunder{John Edwards}, and Teri Peterson. Model selection and regression t-statistics. \textit{The American Statistician}. 72(4), 379-381. 2018.
\begin{IMPACT}
Scopus impact factor: 0.51 % scopus
% CiteScore impact factor: 2.58
%SCI impact factor: 
\end{IMPACT}

Nathan Morrical$^*$ and \pubunder{John Edwards}. Parallel quadtree construction on collections of objects. \textit{Computers and Graphics}. 66:162–168. 2017.
\begin{IMPACT}
Scopus impact factor: 1.63 % scopus
% CiteScore impact factor: 1.7
%SCI impact factor: 
\end{IMPACT}

Boyd Edwards and \pubunder{John Edwards}. Periodic nonlinear sliding modes for two uniformly magnetized spheres. \textit{Chaos: An Interdisciplinary Journal of Nonlinear Science}. 27(5):053107, 2017.
\begin{IMPACT}
Scopus impact factor: 1.76 % scopus
%SCI impact factor: 2.283
\end{IMPACT}

Boyd Edwards and \pubunder{John Edwards}. Dynamical interactions between two uniformly magnetized spheres. \textit{European Journal of Physics}. 38(1):015205, 2016.
\begin{IMPACT}
Scopus impact factor: 0.54 % scopus
%SCI impact factor: 0.614
\end{IMPACT}

Xin Tong, \pubunder{John Edwards}, Chun-Ming Chen, Han-Wei Shen, Christopher Johnson, and Pak Chung Wong. View-dependent streamline deformation and exploration. \textit{IEEE Transactions on Visualization and Computer Graphics}. 22(7):1788-1801, 2016.
\begin{IMPACT}
Scopus impact factor: 3.94 % scopus
% CiteScore impact factor: 4.1
%SCI impact factor: 2.84
\end{IMPACT}

\pubunder{John Edwards}, Eric Daniel, Valerio Pascucci, Chandrajit Bajaj. Approximating the Generalized Voronoi Diagram of Closely Spaced Objects. \textit{Computer Graphics Forum}. 34(2):299-309, 2015.
\begin{IMPACT}
Scopus impact factor: 2.33 % scopus
%SCI impact factor: 1.542
\end{IMPACT}

\pubunder{John Edwards}, Eric Daniel, Justin Kinney, Terrence Sejnowski, Tom Bartol, Daniel Johnston, Kristen Harris, and Chandrajit Bajaj. VolRoverN: Enhancing surface and volumetric reconstruction for realistic dynamical simulation of cellular and subcellular function.  \textit{Neuroinformatics}. 12(2):277-289, 2014.
\begin{IMPACT}
Scopus impact factor: 2.72 % scopus
%SCI impact factor: 2.825
\end{IMPACT}

\begin{footnotesize}$^*$ Student author\end{footnotesize}

%\newpage

\section{\sc Refereed conference publications}

John Edwards, Juho Leinonen, and Arto Hellas. A Study of Keystroke Data in Two Contexts: Written Language and Programming Language Influence Predictability of Learning Outcomes.  \textit{ACM Technical Symposium on Computing Science Education.} Portland, OR. March 2020.  $\sim$30\% acceptance rate.

John Edwards, Erika Fulton, Jonathan Holmes, Joseph Valentin$^*$, David Beard, and Kevin Parker. Separation of syntax and problem solving in Introductory Computer Programming. \textit{IEEE Frontiers in Education.} San Jose, CA. October 2018.  $\sim$50\% acceptance rate.

Sidharth Kumar, Duong Hoang, Steve Petruzza, Valerio Pascucci, and \pubunder{John Edwards}. Reducing network congestion and synchronization overhead during data aggregation when writing hierarchical data. \textit{IEEE International Conference on High Performance Computing, Data, and Analytics.} Jaipur, India. December 2017. 23\% acceptance rate.
%\begin{IMPACT}
%23\% acceptance rate.
%\end{IMPACT}

Nathan Morrical$^*$ and \pubunder{John Edwards}. Parallel quadtree construction on collections of objects. \textit{Shape Modeling International}. Berkeley, CA. June 2017. 37\% acceptance rate.
$^\dagger$
%\begin{IMPACT}
%37\% acceptance rate.
%\end{IMPACT}
%18/49 papers accepted to SMI

\pubunder{John Edwards}, Eric Daniel, Valerio Pascucci, Chandrajit Bajaj. Approximating the Generalized Voronoi Diagram of Closely Spaced Objects. \textit{Eurographics}. Zurich, Switzerland. July 2015. 27\% acceptance rate.
$^\dagger$
%\begin{IMPACT}
%27\% acceptance rate.
%\end{IMPACT}

%Sidharth Kumar, \pubunder{John Edwards}, Peer-Timo Bremer, Aaron Knoll, Cameron Christensen, Venkatram Vishwanath, Philip Carns, John A. Schmidt, Valerio Pascucci. Efficient I/O and storage of adaptive resolution data. \textit{High Performance Computing, Networking, Storage and Analysis (SC14)}. New Orleans, LA. November 2014. 21\% acceptance rate.
%\begin{IMPACT}
%21\% acceptance rate.
%\end{IMPACT}

\begin{footnotesize}$^*$ Student author\end{footnotesize}
\\\begin{footnotesize}$^\dagger$ Also listed under Journals section\end{footnotesize}

\section{\sc Book chapter}

John Edwards, Sidharth Kumar, and Valerio Pascucci. Big data from scientific simulations. In L. Grandinetti, G.R. Joubert, M. Kunze, and V. Pascucci, editors, \textit{Big Data and High Performance Computing}, pages 32--46. IOS Press, Amsterdam, Berlin, Tokyo, Washington, DC, 2015.

\section{\sc Professional service}
Program committee
\vspace{2mm}
%\begin{itemize}[label={},leftmargin=5mm]
\begin{tightitemize1}
  \item IEEE Intermountain Engineering, Technology, and Computing (i-ETC) 2020
  \item International Conference on Geometric Modeling and Processing (GMP) 2015, 2016, 2017, 2018
\end{tightitemize1}

Reviewer
\vspace{2mm}
%\begin{tightitemize}[label={},leftmargin=5mm]
\begin{tightitemize1}
  \item ACM SIGCSE 2019, 2020
  \item Computer Animation and Virtual Worlds
  \item IEEE FIE 2018
  \item ACM Transactions on Mathematical Software
  \item GMP 2015, 2016, 2017, 2018
  \item Computing Surveys
  \item Computer Aided Geometric Design
  \item European Symposium on Algorithms 2014
  \item International Meshing Roundtable 2015
  \item SIGGRAPH Asia 2015
\end{tightitemize1}

\section{\sc University service}
%\vspace{2mm}
%\begin{itemize}[label={},leftmargin=0mm]
\begin{tightitemize0}
%  \setlength\itemsep{0em}
  \item Member of Computer Science Undergraduate Curriculum Committee 2018-2020
  \item Member of Computer Science Faculty Search Committee 2019-2020
  \item Chair of CS faculty search committee 2017-2018 (ISU)
  \item University Research Council 2016-2018 (ISU)
  \item Health Informatics search committee 2016 (ISU)
  \item Author of CS Masters Degree proposal submitted 2018 (ISU)
\end{tightitemize0}

\end{resume}
\end{document}

