\documentclass[margin,line]{res}

\usepackage{version}
\usepackage{versions}
\usepackage{url}
\usepackage{booktabs}
\usepackage{enumitem}
\usepackage[usenames,dvipsnames]{color}

\pagestyle{plain}
%\pagenumbering{arabic}

\setlength{\pdfpagewidth}{\paperwidth}
\setlength{\pdfpageheight}{\paperheight} 

\widowpenalties 1 10000
\raggedbottom

\oddsidemargin -.5in
\evensidemargin -.5in
%\topmargin-2cm
\textwidth=6.0in
\textheight23.5cm
\itemsep=0in
\parsep=0in

\newenvironment{list1}{
  \begin{list}{\ding{113}}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.17in}}}{\end{list}}
\newenvironment{list2}{
  \begin{list}{$\bullet$}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.2in}}}{\end{list}}

%\newcommand{\pubunder}[1]{\underline{#1}}
\newcommand{\pubunder}[1]{#1}

\newcommand{\pnum}[1]{[#1]}
%\newcommand{\pnum}[1]{}
\newcommand{\jnum}[1]{[#1]}
%\newcommand{\jnum}[1]{}
\newcommand{\cnum}[1]{[#1]}
%\newcommand{\cnum}[1]{}

%-------------------------------------------------------------------------------
% this makes list spacing much better.
%-------------------------------------------------------------------------------
\newenvironment{tightenumerate}{
\begin{enumerate}
  \setlength{\itemsep}{1pt}
  \setlength{\parskip}{0pt}
  \setlength{\parsep}{0pt}
}{\end{enumerate}
}

%-------------------------------------------------------------------------------
% this makes list spacing much better.
%-------------------------------------------------------------------------------
\newenvironment{tightitemize}{
\begin{itemize}
  \setlength{\itemsep}{1pt}
  \setlength{\parskip}{0pt}
  \setlength{\parsep}{0pt}
}{\end{itemize}
}

\includeversion{LONG} 
%\excludeversion{LONG} 

%\includeversion{IMPACT}
\excludeversion{IMPACT}

\includeversion{PENDING}
%\excludeversion{PENDING}

\begin{document}

\name{\Large{John Edwards, Ph.D.} \vspace*{.1in}}

\begin{resume}
\section{\sc Contact Information}
\vspace{.05in}
%\begin{tabular}{@{}p{3in}p{3in}}
%\begin{tabular}{@{}p{3.7in}p{3in}}
%Center for Extreme Data Management and Visualization & \\
%Scientific Computing and Imaging Institute   &  \\%801.585.3911 (office)  \\ 
%University of Utah      &  (385) 207-8331 \\
%WEB 4660          &  jedwards@sci.utah.edu \\
%Salt Lake City, UT 84112                &  http://sci.utah.edu/$\sim$jedwards
%\end{tabular}

%\begin{tabular}{@{}p{3.7in}p{3in}}
%Center for Extreme Data Management and Visualization & (385) 207-8331 \\
%Scientific Computing and Imaging Institute   & jedwards@sci.utah.edu \\
%University of Utah      &  http://sci.utah.edu/$\sim$jedwards \\
%WEB 4660          &  \\
%Salt Lake City, UT 84112                & 
%\end{tabular}

\begin{tabular}{@{}p{3.3in}p{3in}}
Department of Computer Science & (435) 797-0246 \\
Utah State University   & john.edwards@usu.edu \\
%MAIN 401D      &  www2.cose.isu.edu/$\sim$edwajohn \\
%MAIN 401D      &  cs.usu.edu/people/faculty/edwards-john \\
MAIN 401D      &  edwardsjohnmartin.github.io \\
Logan, UT 84322          &
\end{tabular}

%\section{\sc Research Interests}
\section{\sc Research}

%Computing education, data visualization, data science
Data visualization, data science, simulation, computing education

\section{\sc Education}

%\textbf{Ph.D.} Computer Science, The University of Texas, 2013\\
%\textbf{M.S.} Computer Science, Brigham Young University, 2004\\
%\textbf{B.S.} Computer Science, Utah State University, 1998\\
Ph.D. Computer Science, The University of Texas, 2013\\
M.S. Computer Science, Brigham Young University, 2004\\
B.S. Computer Science, Utah State University, 1998\\

\section{\sc Professional experience}

Assistant professor, Utah State University, 2018-current\\
Assistant professor, Idaho State University, 2015-2018\\
Post-doctoral fellow, Scientific Computing and Imaging
Institute, University of Utah, 2013-2015\\
Visiting scholar, University of Hong Kong, 2012\\
Assistant instructor (during PhD studies), The University of Texas, 2010-2013\\
Robotics and visualization research engineer, Autonomous Solutions, Inc., 2008-2009\\
Research and development engineer, ProLogic, Inc., 2005-2008 \\
Software engineer, Rigaku, Inc., 1999-2005 \\

\section{\sc Refereed \\ journal publications}% \\ \begin{footnotesize}$^*$ indicates\\student author\end{footnotesize}}
\jnum{18} John Edwards, Kaden Hart$^*$, and Raj Shrestha$^*$. Review of CSEDM Data and Introduction of Two Public CS1 Keystroke Datasets. \textit{Journal of Educational Data Mining.} 2023. Impact factor: 2.15.

\jnum{17} Boyd F Edwards, Cade Pankey, and John M Edwards. Inertial motion on the earth’s spheroidal surface. \textit{Chaos: An Interdisciplinary Journal of Nonlinear Science.} 2022. Impact factor: 2.643. H5-index: 55.

\jnum{16} Bishal Sainju$^*$, Christopher Hartwell, and John Edwards. Job satisfaction and employee turnover determinants in Fortune 50 companies: Insights from employee reviews from Indeed.com. \textit{Decision Support Systems}. 2021. Impact factor: 5.795. H5-index: 65.

\jnum{15} Boyd F Edwards and John M Edwards. Geodetic Model for Teaching Motion on the Earths Spheroidal Surface. \textit{European Journal of Physics}. 2021. Impact factor: 0.756. H5-index: 25.

\jnum{14} John Edwards, Cameron Krome, and Tracy Payne. Computation of Positively Graded Filiform Nilpotent Lie Algebras in Low Dimensions. \textit{Symbolic Computation}. 2021. Impact factor: 0.847. H5-index: 25.

\jnum{13} Boyd Edwards and John Edwards. Forces and Conservation Laws for Motion on our Ellipsoidal Earth. \textit{American Journal of Physics}. 2021. Impact factor: 0.874. H5-index: 20. \textit{Editor's pick.}

\jnum{12} Boyd Edwards, Bo Johnson$^*$, and \pubunder{John Edwards}. Periodic bouncing modes for two uniformly magnetized spheres I: Trajectories. \textit{Chaos: An Interdisciplinary Journal of Nonlinear Science}. 30(1):013146, 2020. Impact factor: 2.643. H5-index: 55. \textit{Featured article.}

\jnum{11} Boyd Edwards, Bo Johnson$^*$, and \pubunder{John Edwards}. Periodic bouncing modes for two uniformly magnetized spheres II: Scaling. \textit{Chaos: An Interdisciplinary Journal of Nonlinear Science}. 30(1):013131, 2020. Impact factor: 2.643. H5-index: 55. 

\jnum{10} Christopher Hartwell, Tyler Orr, and \pubunder{John Edwards}. The Effect of Online Application Efficiency on Applicant Attrition. \textit{International Journal of Selection and Assessment}. 28(2):200-208, 2020. Impact factor: 1.84. H5-index: 19.

\jnum{9} Lloyd Griffel$^*$, Donna Delparte, and John Edwards. Using Support Vector Machines classification to differentiate spectral signatures of potato plants infected with Potato Virus Y. \textit{Computers and electronics in agriculture}, 153:318-324. 2018. Impact factor: 5.565. H5-index: 76.
% CiteScore impact factor: 2.78

\jnum{8} DeWayne Derryberry, Ken Aho, \pubunder{John Edwards}, and Teri Peterson. Model selection and regression t-statistics. \textit{The American Statistician}. 72(4):379-381, 2018. Impact factor: 5.381. H5-index: 39.
\begin{IMPACT}
Scopus impact factor: 0.51 % scopus
% CiteScore impact factor: 2.58
%SCI impact factor: 
\end{IMPACT}

\jnum{7} Nathan Morrical$^*$ and \pubunder{John Edwards}. Parallel quadtree construction on collections of objects. \textit{Computers and Graphics}. 66:162–168. 2017.
\begin{IMPACT}
Scopus impact factor: 1.63 % scopus
% CiteScore impact factor: 1.7
%SCI impact factor: 
\end{IMPACT}

\jnum{6} Boyd Edwards and \pubunder{John Edwards}. Periodic nonlinear sliding modes for two uniformly magnetized spheres. \textit{Chaos: An Interdisciplinary Journal of Nonlinear Science}. 27(5):053107, 2017.
\begin{IMPACT}
Scopus impact factor: 1.76 % scopus
%SCI impact factor: 2.283
\end{IMPACT}

\jnum{5} Boyd Edwards and \pubunder{John Edwards}. Dynamical interactions between two uniformly magnetized spheres. \textit{European Journal of Physics}. 38(1):015205, 2016.
\begin{IMPACT}
Scopus impact factor: 0.54 % scopus
%SCI impact factor: 0.614
\end{IMPACT}

\jnum{4} Xin Tong, \pubunder{John Edwards}, Chun-Ming Chen, Han-Wei Shen, Christopher Johnson, and Pak Chung Wong. View-dependent streamline deformation and exploration. \textit{IEEE Transactions on Visualization and Computer Graphics}. 22(7):1788-1801, 2016.
\begin{IMPACT}
Scopus impact factor: 3.94 % scopus
% CiteScore impact factor: 4.1
%SCI impact factor: 2.84
\end{IMPACT}

\jnum{3} \pubunder{John Edwards}, Eric Daniel, Valerio Pascucci, Chandrajit Bajaj. Approximating the Generalized Voronoi Diagram of Closely Spaced Objects. \textit{Computer Graphics Forum}. 34(2):299-309, 2015.
\begin{IMPACT}
Scopus impact factor: 2.33 % scopus
%SCI impact factor: 1.542
\end{IMPACT}

\jnum{2} \pubunder{John Edwards}, Eric Daniel, Justin Kinney, Terrence Sejnowski, Tom Bartol, Daniel Johnston, Kristen Harris, and Chandrajit Bajaj. VolRoverN: Enhancing surface and volumetric reconstruction for realistic dynamical simulation of cellular and subcellular function.  \textit{Neuroinformatics}. 12(2):277-289, 2014.
\begin{IMPACT}
Scopus impact factor: 2.72 % scopus
%SCI impact factor: 2.825
\end{IMPACT}

\jnum{1} \protect \pubunder{John Edwards} and Chandrajit Bajaj. Topologically correct reconstruction of tortuous contour forests. \textit{Computer-Aided Design}. 43(10):1296-1306, 2011.
\begin{IMPACT}
Scopus impact factor: 2.57 % scopus
%SCI impact factor: 
\end{IMPACT}


\section{\sc Refereed conference publications}
\cnum{36} Joshua Urry$^*$ and John Edwards. A Framework that Explores the Cognitive Load of CS1 Assignments Using Pausing Behavior. \textit{In ACM Technical Symposium on Computing Science Education (SIGCSE).} 2024. Qualis: A2.

\cnum{35} Muhammad Fawad Akbar Khan, John Edwards, Paul Bodily, and Hamid Karimi. Mining Student Behavior Patterns for Enhanced Performance Prediction in Introductory Programming: Keystroke Analysis and Ensemble Strategies. \textit{In IEEE International Conference on Big Data (BigData).} 2023.

\cnum{34} Steven Scott$^*$, Arto Hellas, Juho Leinonen, and John Edwards. Factors Affecting Compilable State at Each Keystroke in CS1. \textit{In ACM International Conference on Software Engineering (ICSE), Software Engineering Education and Training (SEET) track.} 2023. Qualis: A1.

\cnum{33} Kaden Hart$^*$, Christopher Warren, and John Edwards. Accurate Estimation of Time-on-Task While Programming. \textit{In ACM Technical Symposium on Computing Science Education (SIGCSE).} 2023. Qualis: A2.

\cnum{32} Kaden Hart$^*$, Chad Mano, and John Edwards. Plagiarism Deterrence in CS1 Through Keystroke Data. \textit{In ACM Technical Symposium on Computing Science Education (SIGCSE).} 2023. Qualis: A2.

\cnum{31} Arto Hellas, Juho Leinonen, and John Edwards. Code Mimicking: The Impact of Program Output on Novice Programmers’ Learning Gains. \textit{In ACM conference on Innovation and Technology in Computer Science Education (ITiCSE).} 2023. Qualis: B1.

\cnum{30} Aashish Ghimire$^*$, Raj Shrestha$^*$, and John Edwards. Too Legal; Didn’t Read (TLDR): Summarization of Court Opinions. \textit{In IEEE Intermountain Engineering, Technology, and Computing Conference (i-ETC).} 2023.

\cnum{29} Aashish Ghimire$^*$, Rita Ghimire, and John Edwards. Metadata in Tweets: Broadcasting a Lot More Than What You Tweet. \textit{In IEEE Intermountain Engineering, Technology, and Computing Conference (i-ETC).} 2023.

\cnum{28} Stephanie Gonzales$^*$, Hillary Swanson, and John Edwards. Activity During High-Repetition Practice of Syntax. \textit{In IEEE Intermountain Engineering, Technology, and Computing Conference (i-ETC).} 2023.

\cnum{27} Jaxton Winder$^*$, Erik Falor, and John Edwards. Early Submission of Project Analysis Milestones Correlates Positively With Student Project Performance; Incentives for This Early Project Analysis Positively Changes Student Behaviors. \textit{In IEEE Intermountain Engineering, Technology, and Computing Conference (i-ETC).} 2023.

\cnum{26} Raj Shrestha$^*$, Juho Leinonen, Albina Zavgorodniaia, Arto Hellas, and John Edwards. Pausing While Programming: Insights From Keystroke Analysis. \textit{In ACM International Conference on Software Engineering (ICSE), Software Engineering Education and Training (SEET) track.} 2022. Qualis: A1.

\cnum{25} John Edwards, Kaden Hart$^*$, Chris Warren. A practical model of student engagement while programming. \textit{In ACM Technical Symposium on Computing Science Education (SIGCSE).} 2022. Qualis: A2.

\cnum{24} Raj Shrestha$^*$, Juho Leinonen, Arto Hellas, Petri Ihantola, and John Edwards. CodeProcess Charts: Visualizing the Process of Writing Code. \textit{Twenty-Fourth Australasian Computing Education Conference (ACE).} 2022. Qualis: B2.

\cnum{23} Eric Bagley$^*$, Jessica Shumway, and John Edwards. Second-grade Students' Use of Visual Programming to Learn Multiplication: Leveraging the Concept of Iteration. \textit{Twenty-Fourth Australasian Computing Education Conference (ACE).} 2022. Qualis: B2.

\cnum{22} Gordon Fjeldsted$^*$ and John Edwards. Quantifying Student Struggles Using Heatmaps and Keystroke Data. \textit{IEEE Intermountain Engineering, Technology, and Computing Conference (i-ETC).} 2022.

\cnum{21} Aashish Ghimire$^*$ and John Edwards. Introspection with Data: Using Personality Traits for Academic Major Selection. \textit{IEEE Intermountain Engineering, Technology, and Computing Conference (i-ETC).} 2022.

\cnum{20} Marina Johnson$^*$, Hillary Swanson, and John Edwards. Syntax Exercises and Their Effect on Computational Thinking. \textit{IEEE Intermountain Engineering, Technology, and Computing Conference (i-ETC).} 2022.

\cnum{19} Delaney Moore, John Edwards, Hamid Karimi, Rajiv Khadka, and Paul Bodily. Temporal Abstract Syntax Trees for Understanding Student Coding Thought Process. \textit{IEEE Intermountain Engineering, Technology, and Computing Conference (i-ETC).} 2022.

\cnum{18} Shelsey Sullivan$^*$, Hillary Swanson, and John Edwards. Student attitudes toward syntax exercises in CS1. \textit{In ACM Technical Symposium on Computing Science Education (SIGCSE).} 2021. Acceptance rate: 34\%. Qualis: A2.

\cnum{17} Joseph Ditton$^*$, Hillary Swanson, and John Edwards. External imagery in computer programming. \textit{In ACM Technical Symposium on Computing Science Education (SIGCSE).} 2021. Acceptance rate: 34\%. Qualis: A2.

\cnum{16} Albina Zavgorodniaia, Raj Shrestha$^*$, Juho Leinonen, Arto Hellas, and John Edwards. Morning or Evening? An Examination of Circadian Rhythms of CS1 Students. \textit{In ACM International Conference on Software Engineering (ICSE), Joint Track on Software Engineering Education and Training (JSEET)}. 2021. Acceptance rate: 33\%. Qualis: A1.

\cnum{15} Anna Ly, John Edwards, Michael Liut, and Andrew Petersen. Revisiting Syntax Exercises in CS1. \textit{ACM Conference on Information Technology Education (SIGITE).} 2021. Acceptance rate: 48\%. Qualis: B3.

\cnum{14} John Edwards, Joseph Ditton$^*$, Dragan Trninic, Shelsey Sullivan$^*$, Hillary Swanson, and Chad Mano. Syntax exercises in CS1. \textit{ACM International Computing Education Research (ICER) Conference.} Dunedin, New Zealand. August 2020. Acceptance rate: 23\%. Qualis: B4.

\cnum{13} John Edwards, Juho Leinonen, Albina Zavgorodniaia, Chetan Birthare$^*$, and Arto Hellas. Programming versus natural language: on the effect of context on typing in CS1. \textit{ACM International Computing Education Research (ICER) Conference.} Dunedin, New Zealand. August 2020. Acceptance rate: 23\%. Qualis: B4.

\cnum{12} Steven Scott$^*$, Jaxon Willard$^*$, and \pubunder{John Edwards}. High Dimensional Event Exploration over Multiple Simulations. \textit{IEEE Intermountain Engineering, Technology, and Computing Conference (i-ETC).} Orem, UT. September, 2020. Acceptance rate: 86\%.

\cnum{11} John Edwards, Joseph Ditton$^*$, Bishal Sainju$^*$, and Joshua Dawson$^*$. Different Assignments as Different Contexts: Predictors Across Assignments and Outcome Measures in CS1. \textit{IEEE Intermountain Engineering, Technology, and Computing Conference (i-ETC).} Orem, UT. September, 2020. Acceptance rate: 86\%.

\cnum{10} John Edwards, Juho Leinonen, and Arto Hellas. A Study of Keystroke Data in Two Contexts: Written Language and Programming Language Influence Predictability of Learning Outcomes.  \textit{ACM Technical Symposium on Computing Science Education (SIGCSE).} Portland, OR. March 2020.  Acceptance rate: 31\%. Qualis: A2.

\cnum{9} John Edwards, Erika Fulton, Jonathan Holmes, Joseph Valentin$^*$, David Beard, and Kevin Parker. Separation of syntax and problem solving in Introductory Computer Programming. \textit{IEEE Frontiers in Education.} San Jose, CA. October 2018.  Acceptance rate: $\sim$50\%. Qualis: B1.

\cnum{8} Sidharth Kumar, Duong Hoang, Steve Petruzza, Valerio Pascucci, and \pubunder{John Edwards}. Reducing network congestion and synchronization overhead during data aggregation when writing hierarchical data. \textit{IEEE International Conference on High Performance Computing, Networking, Storage, and Analysis.} Jaipur, India. December 2017. 23\% acceptance rate. H5-index: 43.
%\begin{IMPACT}
%23\% acceptance rate.
%\end{IMPACT}

\cnum{7} Nathan Morrical$^*$ and \pubunder{John Edwards}. Parallel quadtree construction on collections of objects. \textit{Shape Modeling International}. Berkeley, CA. June 2017. 37\% acceptance rate.
$^\dagger$
%\begin{IMPACT}
%37\% acceptance rate.
%\end{IMPACT}
%18/49 papers accepted to SMI

\cnum{6} \pubunder{John Edwards}, Eric Daniel, Valerio Pascucci, Chandrajit Bajaj. Approximating the Generalized Voronoi Diagram of Closely Spaced Objects. \textit{Eurographics}. Zurich, Switzerland. July 2015. 27\% acceptance rate. H5-index: 10.
$^\dagger$
%\begin{IMPACT}
%27\% acceptance rate.
%\end{IMPACT}

\cnum{5} Sidharth Kumar, \pubunder{John Edwards}, Peer-Timo Bremer, Aaron Knoll, Cameron Christensen, Venkatram Vishwanath, Philip Carns, John A. Schmidt, Valerio Pascucci. Efficient I/O and storage of adaptive resolution data. \textit{High Performance Computing, Networking, Storage and Analysis (SC14)}. New Orleans, LA. November 2014. 21\% acceptance rate. H5-index: 43.
%\begin{IMPACT}
%21\% acceptance rate.
%\end{IMPACT}

\cnum{4} \pubunder{John Edwards}, Wenping Wang, and Chandrajit Bajaj. Surface segmentation for improved remeshing. \textit{Proceedings of the 21st International Meshing Roundtable}, pages 403-418. San Jose, CA. October 2012.

\cnum{3} \pubunder{John Edwards} and Chandrajit Bajaj. Topologically correct reconstruction of tortuous contour forests. \textit{Proceedings of the ACM Symposium on Solid and Physical Modeling}, pages 51-60. Haifa, Israel. September 2010. 29\% acceptance rate.
%\begin{IMPACT}
%29\% acceptance rate.
%% 51 submitted, 15 full papers accepted (11 short papers accepted) for 29\% acceptance rate
%\end{IMPACT}

\cnum{2} Joel Alberts, \pubunder{John Edwards}, Josh Johnston, and Jeff Ferrin. 3D visualization for improved manipulation and mobility in EOD and combat engineering applications. \textit{Proceedings of SPIE Defense, Security and Sensing}. April 2009.

\cnum{1} Josh Johnston, Joel Alberts, Matt Berkemeier, and \pubunder{John Edwards}. Manipulator Autonomy for EOD Robots. \textit{26th Army Science Conference}. December 2008.
%% <www.edwardssoftware.com/john/ManipulatorAutonomy.pdf>

%\section{\sc Papers in review}
%\cnum{6} Aashish Ghimire$^*$, James Prather, and \pubunder{John Edwards}. Attitudes toward Generative AI in Education. \textit{In review.}

%\cnum{5} Logan Hendricks$^*$ and \pubunder{John Edwards}. White-Label Bootcamps -- Branding and Opinions. \textit{In review.}

%\cnum{4} Logan Hendricks$^*$ and \pubunder{John Edwards}. Coding Bootcamps: Employment Outcomes. \textit{In review.}

%\cnum{3} Kaden Hart$^*$, Chris Warren, and \pubunder{John Edwards}. Phone usage while programming. \textit{In review.}

%\cnum{2} Joshua Urry$^*$ and \pubunder{John Edwards}. A Framework that Explores the Cognitive Load of CS1 Assignments Using Pausing Behavior. \textit{In review.}

%\cnum{1} Jaxton Winder$^*$, Elise Francis$^*$, Bridget Staley$^*$, and \pubunder{John Edwards}. Measure of Incremental Development on CS1 Outcomes And Behaviors. \textit{In review.}

%\cnum{2} Kaden Hart$^*$, Chris Warren, and \pubunder{John Edwards}. Post-activity estimation of time-on-task. \textit{In final preparation.}

%\cnum{1} Chris Brown$^*$, Steven Scott$^*$, and \pubunder{John Edwards}. Abstract Syntax Tree Tracking Through Time. \textit{In final preparation.}


%%\section{\sc Peer-reviewed publications}
%%\vspace{1.2cm}
%\section{\sc Publications}
%
%\begin{footnotesize}$^*$ Student author\end{footnotesize}
%%\\\begin{footnotesize}$^\dagger$ Extended journal version also listed\end{footnotesize}
%%\\\begin{footnotesize}Impact measures explained after listing\end{footnotesize}
%
%\textbf{2023} \\
%\pnum{47} Steven Scott$^*$, Arto Hellas, Juho Leinonen, and John Edwards. Factors Affecting Compilable State at Each Keystroke in CS1. \textit{In ACM International Conference on Software Engineering (ICSE), Software Engineering Education and Training (SEET) track.} 2023. Qualis: A1.
%
%\pnum{46} John Edwards, Kaden Hart$^*$, and Raj Shrestha$^*$. Review of CSEDM Data and Introduction of Two Public CS1 Keystroke Datasets. \textit{Journal of Educational Data Mining.} 2023. Impact factor: 2.15.
%
%\pnum{45} Kaden Hart$^*$, Christopher Warren, and John Edwards. Accurate Estimation of Time-on-Task While Programming. \textit{In ACM Technical Symposium on Computing Science Education (SIGCSE).} 2023. Qualis: A2.
%
%\pnum{44} Kaden Hart$^*$, Chad Mano, and John Edwards. Plagiarism Deterrence in CS1 Through Keystroke Data. \textit{In ACM Technical Symposium on Computing Science Education (SIGCSE).} 2023. Qualis: A2.
%
%\textbf{2022} \\
%\pnum{43} Boyd F Edwards, Cade Pankey, and John M Edwards. Inertial motion on the earth’s spheroidal surface. \textit{Chaos: An Interdisciplinary Journal of Nonlinear Science.} 2022. Impact factor: 2.643. H5-index: 55.
%
%\pnum{42} Raj Shrestha$^*$, Juho Leinonen, Albina Zavgorodniaia, Arto Hellas, and John Edwards. Pausing While Programming: Insights From Keystroke Analysis. \textit{In ACM International Conference on Software Engineering (ICSE), Software Engineering Education and Training (SEET) track.} 2022. Qualis: A1.
%
%\pnum{41} John Edwards, Kaden Hart$^*$, Chris Warren. A practical model of student engagement while programming. \textit{In ACM Technical Symposium on Computing Science Education (SIGCSE).} 2022. Qualis: A2.
%
%\pnum{40} Raj Shrestha$^*$, Juho Leinonen, Arto Hellas, Petri Ihantola, and John Edwards. CodeProcess Charts: Visualizing the Process of Writing Code. \textit{Twenty-Fourth Australasian Computing Education Conference (ACE).} 2022. Qualis: B2.
%
%\pnum{39} Eric Bagley$^*$, Jessica Shumway, and John Edwards. Second-grade Students' Use of Visual Programming to Learn Multiplication: Leveraging the Concept of Iteration. \textit{Twenty-Fourth Australasian Computing Education Conference (ACE).} 2022. Qualis: B2.
%
%\pnum{38} Gordon Fjeldsted$^*$ and John Edwards. Quantifying Student Struggles Using Heatmaps and Keystroke Data. \textit{IEEE Intermountain Engineering, Technology, and Computing Conference (i-ETC).} 2022.
%
%\pnum{37} Aashish Ghimire$^*$ and John Edwards. Introspection with Data: Using Personality Traits for Academic Major Selection. \textit{IEEE Intermountain Engineering, Technology, and Computing Conference (i-ETC).} 2022.
%
%\pnum{36} Marina Johnson$^*$, Hillary Swanson, and John Edwards. Syntax Exercises and Their Effect on Computational Thinking. \textit{IEEE Intermountain Engineering, Technology, and Computing Conference (i-ETC).} 2022.
%
%\pnum{35} Delaney Moore, John Edwards, Hamid Karimi, Rajiv Khadka, and Paul Bodily. Temporal Abstract Syntax Trees for Understanding Student Coding Thought Process. \textit{IEEE Intermountain Engineering, Technology, and Computing Conference (i-ETC).} 2022.
%
%\textbf{2021} \\
%\pnum{34} Shelsey Sullivan$^*$, Hillary Swanson, and John Edwards. Student attitudes toward syntax exercises in CS1. \textit{In ACM Technical Symposium on Computing Science Education (SIGCSE).} 2021. Acceptance rate: 34\%. Qualis: A2.
%
%\pnum{33} Joseph Ditton$^*$, Hillary Swanson, and John Edwards. External imagery in computer programming. \textit{In ACM Technical Symposium on Computing Science Education (SIGCSE).} 2021. Acceptance rate: 34\%. Qualis: A2.
%
%\pnum{32} Bishal Sainju$^*$, Christopher Hartwell, and John Edwards. Job satisfaction and employee turnover determinants in Fortune 50 companies: Insights from employee reviews from Indeed.com. \textit{Decision Support Systems}. 2021. Impact factor: 5.795. H5-index: 65.
%
%\pnum{31} Albina Zavgorodniaia, Raj Shrestha$^*$, Juho Leinonen, Arto Hellas, and John Edwards. Morning or Evening? An Examination of Circadian Rhythms of CS1 Students. \textit{In ACM International Conference on Software Engineering (ICSE), Joint Track on Software Engineering Education and Training (JSEET)}. 2021. Acceptance rate: 33\%. Qualis: A1.
%
%\pnum{30} Anna Ly, John Edwards, Michael Liut, and Andrew Petersen. Revisiting Syntax Exercises in CS1. \textit{ACM Conference on Information Technology Education (SIGITE).} 2021. Acceptance rate: 48\%. Qualis: B3.
%
%\pnum{29} Boyd F Edwards and John M Edwards. Geodetic Model for Teaching Motion on the Earths Spheroidal Surface. \textit{European Journal of Physics}. 2021. Impact factor: 0.756. H5-index: 25.
%
%\pnum{28} John Edwards, Cameron Krome, and Tracy Payne. Computation of Positively Graded Filiform Nilpotent Lie Algebras in Low Dimensions. \textit{Symbolic Computation}. 2021. Impact factor: 0.847. H5-index: 25.
%
%\pnum{27} Boyd Edwards and John Edwards. Forces and Conservation Laws for Motion on our Ellipsoidal Earth. \textit{American Journal of Physics}. 2021. Impact factor: 0.874. H5-index: 20. \textit{Editor's pick.}
%
%% 93 submissions, 31 accepted
%
%\textbf{2020} \\
%\pnum{26} John Edwards, Joseph Ditton$^*$, Dragan Trninic, Shelsey Sullivan$^*$, Hillary Swanson, and Chad Mano. Syntax exercises in CS1. \textit{ACM International Computing Education Research (ICER) Conference.} Dunedin, New Zealand. August 2020. Acceptance rate: 23\%. Qualis: B4.
%
%\pnum{25} John Edwards, Juho Leinonen, Albina Zavgorodniaia, Chetan Birthare$^*$, and Arto Hellas. Programming versus natural language: on the effect of context on typing in CS1. \textit{ACM International Computing Education Research (ICER) Conference.} Dunedin, New Zealand. August 2020. Acceptance rate: 23\%. Qualis: B4.
%
%\pnum{24} Steven Scott$^*$, Jaxon Willard$^*$, and \pubunder{John Edwards}. High Dimensional Event Exploration over Multiple Simulations. \textit{IEEE Intermountain Engineering, Technology, and Computing Conference (i-ETC).} Orem, UT. September, 2020. Acceptance rate: 86\%.
%
%\pnum{23} John Edwards, Joseph Ditton$^*$, Bishal Sainju$^*$, and Joshua Dawson$^*$. Different Assignments as Different Contexts: Predictors Across Assignments and Outcome Measures in CS1. \textit{IEEE Intermountain Engineering, Technology, and Computing Conference (i-ETC).} Orem, UT. September, 2020. Acceptance rate: 86\%.
%
%\pnum{22} Boyd Edwards, Bo Johnson$^*$, and \pubunder{John Edwards}. Periodic bouncing modes for two uniformly magnetized spheres I: Trajectories. \textit{Chaos: An Interdisciplinary Journal of Nonlinear Science}. 30(1):013146, 2020. Impact factor: 2.643. H5-index: 55. \textit{Featured article.}
%
%\pnum{21} Boyd Edwards, Bo Johnson$^*$, and \pubunder{John Edwards}. Periodic bouncing modes for two uniformly magnetized spheres II: Scaling. \textit{Chaos: An Interdisciplinary Journal of Nonlinear Science}. 30(1):013131, 2020. Impact factor: 2.643. H5-index: 55. 
%
%\pnum{20} Christopher Hartwell, Tyler Orr, and \pubunder{John Edwards}. The Effect of Online Application Efficiency on Applicant Attrition. \textit{International Journal of Selection and Assessment}. 28(2):200-208, 2020. Impact factor: 1.84. H5-index: 19.
%
%\pnum{19} John Edwards, Juho Leinonen, and Arto Hellas. A Study of Keystroke Data in Two Contexts: Written Language and Programming Language Influence Predictability of Learning Outcomes.  \textit{ACM Technical Symposium on Computing Science Education (SIGCSE).} Portland, OR. March 2020.  Acceptance rate: 31\%. Qualis: A2.
%
%\textbf{2018} \\
%\pnum{18} John Edwards, Erika Fulton, Jonathan Holmes, Joseph Valentin$^*$, David Beard, and Kevin Parker. Separation of syntax and problem solving in Introductory Computer Programming. \textit{IEEE Frontiers in Education.} San Jose, CA. October 2018.  Acceptance rate: $\sim$50\%. Qualis: B1.
%
%\pnum{17} Lloyd Griffel$^*$, Donna Delparte, and John Edwards. Using Support Vector Machines classification to differentiate spectral signatures of potato plants infected with Potato Virus Y. \textit{Computers and electronics in agriculture}, 153:318-324. 2018. Impact factor: 5.565. H5-index: 76.
%% CiteScore impact factor: 2.78
%
%\pnum{16} DeWayne Derryberry, Ken Aho, \pubunder{John Edwards}, and Teri Peterson. Model selection and regression t-statistics. \textit{The American Statistician}. 72(4):379-381, 2018. Impact factor: 5.381. H5-index: 39.
%\begin{IMPACT}
%Scopus impact factor: 0.51 % scopus
%% CiteScore impact factor: 2.58
%%SCI impact factor: 
%\end{IMPACT}
%
%\textbf{2017} \\
%\pnum{15} Nathan Morrical$^*$ and \pubunder{John Edwards}. Parallel quadtree construction on collections of objects. \textit{Computers and Graphics}. 66:162–168. 2017.
%\begin{IMPACT}
%Scopus impact factor: 1.63 % scopus
%% CiteScore impact factor: 1.7
%%SCI impact factor: 
%\end{IMPACT}
%
%\pnum{14} Boyd Edwards and \pubunder{John Edwards}. Periodic nonlinear sliding modes for two uniformly magnetized spheres. \textit{Chaos: An Interdisciplinary Journal of Nonlinear Science}. 27(5):053107, 2017.
%\begin{IMPACT}
%Scopus impact factor: 1.76 % scopus
%%SCI impact factor: 2.283
%\end{IMPACT}
%
%\pnum{13} Sidharth Kumar, Duong Hoang, Steve Petruzza, Valerio Pascucci, and \pubunder{John Edwards}. Reducing network congestion and synchronization overhead during data aggregation when writing hierarchical data. \textit{IEEE International Conference on High Performance Computing, Networking, Storage, and Analysis.} Jaipur, India. December 2017. 23\% acceptance rate. H5-index: 43.
%%\begin{IMPACT}
%%23\% acceptance rate.
%%\end{IMPACT}
%
%\pnum{12} Nathan Morrical$^*$ and \pubunder{John Edwards}. Parallel quadtree construction on collections of objects. \textit{Shape Modeling International}. Berkeley, CA. June 2017. 37\% acceptance rate.
%$^\dagger$
%%\begin{IMPACT}
%%37\% acceptance rate.
%%\end{IMPACT}
%%18/49 papers accepted to SMI
%
%\textbf{2016} \\
%\pnum{11} Boyd Edwards and \pubunder{John Edwards}. Dynamical interactions between two uniformly magnetized spheres. \textit{European Journal of Physics}. 38(1):015205, 2016.
%\begin{IMPACT}
%Scopus impact factor: 0.54 % scopus
%%SCI impact factor: 0.614
%\end{IMPACT}
%
%\pnum{10} Xin Tong, \pubunder{John Edwards}, Chun-Ming Chen, Han-Wei Shen, Christopher Johnson, and Pak Chung Wong. View-dependent streamline deformation and exploration. \textit{IEEE Transactions on Visualization and Computer Graphics}. 22(7):1788-1801, 2016.
%\begin{IMPACT}
%Scopus impact factor: 3.94 % scopus
%% CiteScore impact factor: 4.1
%%SCI impact factor: 2.84
%\end{IMPACT}
%
%\textbf{2015} \\
%\pnum{9} \pubunder{John Edwards}, Eric Daniel, Valerio Pascucci, Chandrajit Bajaj. Approximating the Generalized Voronoi Diagram of Closely Spaced Objects. \textit{Computer Graphics Forum}. 34(2):299-309, 2015.
%\begin{IMPACT}
%Scopus impact factor: 2.33 % scopus
%%SCI impact factor: 1.542
%\end{IMPACT}
%
%\pnum{8} \pubunder{John Edwards}, Eric Daniel, Valerio Pascucci, Chandrajit Bajaj. Approximating the Generalized Voronoi Diagram of Closely Spaced Objects. \textit{Eurographics}. Zurich, Switzerland. July 2015. 27\% acceptance rate. H5-index: 10.
%$^\dagger$
%%\begin{IMPACT}
%%27\% acceptance rate.
%%\end{IMPACT}
%
%\textbf{2014} \\
%\pnum{7} Sidharth Kumar, \pubunder{John Edwards}, Peer-Timo Bremer, Aaron Knoll, Cameron Christensen, Venkatram Vishwanath, Philip Carns, John A. Schmidt, Valerio Pascucci. Efficient I/O and storage of adaptive resolution data. \textit{High Performance Computing, Networking, Storage and Analysis (SC14)}. New Orleans, LA. November 2014. 21\% acceptance rate. H5-index: 43.
%%\begin{IMPACT}
%%21\% acceptance rate.
%%\end{IMPACT}
%
%\pnum{6} \pubunder{John Edwards}, Eric Daniel, Justin Kinney, Terrence Sejnowski, Tom Bartol, Daniel Johnston, Kristen Harris, and Chandrajit Bajaj. VolRoverN: Enhancing surface and volumetric reconstruction for realistic dynamical simulation of cellular and subcellular function.  \textit{Neuroinformatics}. 12(2):277-289, 2014.
%\begin{IMPACT}
%Scopus impact factor: 2.72 % scopus
%%SCI impact factor: 2.825
%\end{IMPACT}
%
%\textbf{$\le$2012} \\
%\pnum{5} \pubunder{John Edwards}, Wenping Wang, and Chandrajit Bajaj. Surface segmentation for improved remeshing. \textit{Proceedings of the 21st International Meshing Roundtable}, pages 403-418. San Jose, CA. October 2012.
%
%\pnum{4} \protect \pubunder{John Edwards} and Chandrajit Bajaj. Topologically correct reconstruction of tortuous contour forests. \textit{Computer-Aided Design}. 43(10):1296-1306, 2011.
%\begin{IMPACT}
%Scopus impact factor: 2.57 % scopus
%%SCI impact factor: 
%\end{IMPACT}
%
%\pnum{3} \pubunder{John Edwards} and Chandrajit Bajaj. Topologically correct reconstruction of tortuous contour forests. \textit{Proceedings of the ACM Symposium on Solid and Physical Modeling}, pages 51-60. Haifa, Israel. September 2010. 29\% acceptance rate.
%%\begin{IMPACT}
%%29\% acceptance rate.
%%% 51 submitted, 15 full papers accepted (11 short papers accepted) for 29\% acceptance rate
%%\end{IMPACT}
%
%\pnum{2} Joel Alberts, \pubunder{John Edwards}, Josh Johnston, and Jeff Ferrin. 3D visualization for improved manipulation and mobility in EOD and combat engineering applications. \textit{Proceedings of SPIE Defense, Security and Sensing}. April 2009.
%
%\pnum{1} Josh Johnston, Joel Alberts, Matt Berkemeier, and \pubunder{John Edwards}. Manipulator Autonomy for EOD Robots. \textit{26th Army Science Conference}. December 2008.
%%% <www.edwardssoftware.com/john/ManipulatorAutonomy.pdf>
%
%\begin{IMPACT}
%% * Scopus impact factors used
%\end{IMPACT}

\begin{footnotesize}$^*$ indicates student author\end{footnotesize}
%\begin{footnotesize}$^*$ Student author\end{footnotesize}
%\\\begin{footnotesize}$^\dagger$ Extended journal version also listed\end{footnotesize}

\begin{footnotesize}
Publication quality metrics:
\vspace{-.4cm}
\begin{tightitemize}
\item Impact factor - Impact factor for year $y$ calculated as $(c_{y-1}+c_{y-2})/(p_{y-1}+p_{y-2})$ where $c_y$ is the number of citations and $p_y$ is the number of publications for year $y$.
\item H5-Index - The Google Scholar H5-Index is the largest number $h$ such that $h$ articles published in the last 5 years have at least $h$ citations each.
\item Qualis (conference) - Qualis ranks are obtained from www.conferenceranks.com and have possible values of A1, A2, B1, B2, B3, B4, and B5.
\end{tightitemize}
\end{footnotesize}


%\newpage

%\section{\sc Refereed conference publications}

%John Edwards. LiveMesh: An Interactive 3D Image Segmentation Tool. Masters Thesis, December 2004.
%% <www.edwardssoftware.com/john/Thesis.pdf>

\section{\sc Book chapter}

John Edwards, Sidharth Kumar, and Valerio Pascucci. Big data from scientific simulations. In L. Grandinetti, G.R. Joubert, M. Kunze, and V. Pascucci, editors, \textit{Big Data and High Performance Computing}, pages 32--46. IOS Press, Amsterdam, Berlin, Tokyo, Washington, DC, 2015.

%\begin{PENDING}
%\section{\sc Pending publications}
%
%\end{PENDING}

%\section{\sc Submitted}

%John Edwards, Joshua Dawson, Joseph Ditton, Bishal Sainju. Predictors across assignments and success measures in CS1. \textit{Submitted}. 2019.

%John Edwards, Erika Fulton, Jonathan Holmes, Joseph Valentin, David Beard, Kevin Parker. Separating syntax and problem solving in CS1. \textit{Submitted}. 2019.

\section{\sc Funding}
%\begin{itemize}[label={},leftmargin=0pt]
%  \setlength\itemsep{0.5em}
%\item Won: \$184,017\\Pending: \$248,304
%\item Won: \$184,017 (\$22,842 as PI)\\Pending: \$1,135,880 (\$235,740 as PI)
%\item Won: \$184K (\$23K as PI)\\Pending: \$1.1m (\$236K as PI)
%\section{\sc Funded (\$184,017)}
%\item \underline{Funded (\$184,017)}
\textit{How novices write code: discovering best practices and how they can be adopted}. PI: \underline{J. Edwards}. National Science Foundation (NSF). Award \#2315783. \$238,468. 2023-2026.

\textit{DynamicsLab: Interactive Physics Simulations for Intermediate Classical Mechanics}. PI: \underline{J. Edwards}. co-PIs: H. Swanson, B. Edwards. National Science Foundation (NSF). Award \#2235569. \$299,649. 2023-2026.

\textit{Revolutionary Data Presentation and Manipulation}. PI: M. Shields. co-PIs: \underline{J. Edwards}, D. Heath. Missile Defense Agency (STTR). B18C-001-0097. \$100,000. 2018.

\textit{Syntax before problem solving: an approach to introductory computer programming education}. PI: \underline{J. Edwards}. co-PIs: E. Fulton, J. Holmes, D. Beard, K. Parker. Idaho State University Office of Research. \$32,564. 2017.

\textit{Implementing Unmanned Aircraft Systems to detect crop viruses using hyperspectral remote sensing and machine learning}. PI: D. Delparte. co-PI: \underline{J. Edwards}. Idaho State Dept. of Agriculture. \$161,175. 2017.

%\textit{Unified modeling and visualization of avalanche flow paths}. PI: \underline{J. Edwards} with S. Pawlidis (student). STEM Undergraduate Research Initiative, Idaho SBOE. \$1,740. 2017.

%\textit{ISU CoSE Internal Travel Grant}. \underline{J. Edwards}. \$2,000. 2017.

\textit{Improving STEM Education: Engaged Learning in an Introductory  Computer Programming Course}. PI: \underline{J. Edwards}. co-PIs: J. Holmes, K. Parker. ISU Teaching Innovation Grant. \$4820. 2017.

\textit{STEM Action Center: Computer Programming Workshops in Southeastern Idaho}. C. Hill, et al. United Way. \$8000. Role: Senior personnel. 2017.

\textit{igniteCS: CS education in Southeastern Idaho high schools}. PI: \underline{J. Edwards} co-PIs: J. Rose, J. Glines, et al. Google igniteCS gift. \$5307. 2016.

%\textit{NIH BRAIN Initiative Summer Course on interdisciplinary computational neuroscience}. \underline{J. Edwards}. Competitive admission to funded workshop at University of Missouri. 31\% acceptance rate. 2016. % 31% acceptance rate (24/77)

%\textit{UTexas Professional Development Award for travel to San Jose, CA}. \underline{J. Edwards}. \$275. 2012. %(\$275)

%\textit{UTexas Professional Development Award for travel to Providence, RI}. \underline{J. Edwards}. \$250. 2011. %(\$275)

%\textit{UTexas Professional Development Award for travel to Haifa, Israel}. \underline{J. Edwards}. \$450. 2010. %(\$275)
%\end{itemize}

%\section{\sc Grants pending}
%\textit{Collaborative Research: Sustainable professional development of high school computer programming teachers using syntax scaffolding}. PI: \underline{J. Edwards}. co-PI: Mimi Recker. NSF 17-584. \$119,264 (\$271,974 total). 2018.

%\section{\sc Grants not funded}
%\textit{Web-Based Simulations for Intermediate Mechanics Education}. PI: \underline{J. Edwards}. co-PI: S. Shropshire. NSF 17-561. \$215,740. 2017. Not funded.
%
%\textit{In-situ plant virus detection system using advanced remote sensing and machine learning}. PI: D. Delparte. co-PI: \underline{J. Edwards}. NSF 17-529. \$900,140. 2017. Not funded.
%
%\textit{Sensor Systems for Decision Support in the Food, Energy and Water Nexus - Testbed in Idaho's Snake River Plain}. PI: D. Delparte. co-PIs: C. Baxter, S. Godsey, F. Harris, D. Van Horn J. Rachlow, J. Forbey, \underline{J. Edwards}. NSF15-517. \$5,999,723. 2015. Not funded. %(Co-PI) % NSF 15-517 is the solicitation. \$5,999,723
%
%\textit{iSEED: UAS to Advance SES Modeling.}. PI: J. Johnston. co-PIs: J. Forbey, L. Vierling, J. Eitel, \underline{J. Edwards}, D. Delparte. NSF EPSCoR Managing Idaho’s Landscapes for Ecosystem Services (MILES) iSEED. \$242,976. 2015. Not funded. % \$242,976.07
%
%\textit{MRI: Acquisition of advanced Unmanned Aircraft Systems (UAS) remote imaging sensors and ground-based spectrometry for understanding structural and phytochemical function of ecosystems.}. PI: D. Delparte. co-PIs: \underline{J. Edwards}, J. Rachlow, J. Forbey. NSF15-504. 2015. Not funded. % 15-504 is the solicitation
%
%\textit{Morse Smale Crystals as Meshing Primitives for Lagrangian Simulations}. PI: P-T. Bremer. co-PIs: V. Pascucci, \underline{J. Edwards}, A. Gyulassy. DOE LAB 14-1003. 2013. Not funded.

\section{\sc Pending grants}
\textit{How novices write code: discovering best practices and how they can be adopted}. PI: \underline{J. Edwards}. National Science Foundation (NSF). \emph{Recommended for funding}. \$238,468. 2023-2026.

\textit{DTI: Nurturing Family Support in Middle School Coding Programs}. PI: Vicki Allan. co-PIs: \underline{J. Edwards}, Deborah Sue Ivie, Rebecca Bayeck. National Science Foundation (NSF). \emph{In review}. \$1,299,999.62. 2024-2028.


\section{\sc Theses}
(Ph.D.) Analysis-Ready Models of Tortuous, Tightly Packed Geometries, 2013\\
(M.S.) Live Mesh: An Interactive 3D Image Segmentation Tool, 2004

%\section{\sc Thesis}
%Analysis-Ready Models of Tortuous, Tightly Packed Geometries, 2013\\

\section{\sc Licensed Software}

\emph{CodeKeyz} (originally named \emph{Phanon}) - CS1 Education Software\\
\url{https://codekeyz.com}

\section{\sc Research Software and Datasets}

\emph{KeystrokeExplorer} - Keystroke log analysis software\\
\url{https://edwardsjohnmartin.github.io/KeystrokeExplorer/}

\emph{Two keystroke datasets} - Keystroke log datasets (1,275 downloads as of July 27, 2023)\\
\url{https://doi.org/10.7910/DVN/BVOF7S}\\
\url{https://doi.org/10.7910/DVN/6BPCXN}

\emph{DynamicsLab} - Physics education software\\
\url{ https://edwardslabusu.github.io/DynamicsLab}

\emph{CorioVis} - Coriolis simulation software\\
\url{https://edwardsjohnmartin.github.io/coriolis}

%\emph{avalanche} - Avalanche simulation software\\
%\url{https://github.com/edwardsjohnmartin/avalanche.git}

\emph{MagPhyx} - Magnet simulation software\\
\url{http://edwardsjohnmartin.github.io/MagPhyx}

%\emph{GVD} - Generalized Voronoi Diagram approximation\\
%\url{http://www2.cose.isu.edu/~edwajohn/research/gvd}

\emph{pgvd} - Parallel Generalized Voronoi Diagram Approximation\\
\url{https://github.com/edwardsjohnmartin/pgvd.git}

\emph{VolRoverN} - Neuronal reconstruction and geometric analysis\\
\url{http://www.cs.utexas.edu/$\sim$bajaj/cvcwp/?page\_id=2089}

%\emph{SimpleSeg} - Image segmentation in 3D using LiveMesh (no longer maintained)\\
%http://www.youtube.com/watch?v=9KfhFvIvFK4
%http://www.edwardssoftware.com/john

%\begin{LONG}
%
%\section{\sc Posters}
%%\section{\sc Posters\\$\star$ Best poster award}
%B. Johnson, B. Edwards, J. Edwards.
%Dynamical Interactions between Two Uniformly Magnetized Spheres
%\textit{American Physical Society Four Corners Section: Annual Meeting}. Salt Lake City, UT, October 2018.
%
%J. Ory, W. Grigg, J. Edwards, J. Holmes, K. Parker.
%3PIO: Powerful and Practical Python IDE Online
%\textit{Idaho Conference on Undergraduate Research}. Boise, ID, July 2017.
%
%W. Grigg, S. Denton, J. Edwards, J. Stover.
%Hidden associations: visualizing word-to-word connections in Tweets
%\textit{Idaho Conference on Undergraduate Research}. Boise, ID, July 2017.
%
%J. Valentin, K. Aho, J. Edwards, D. Derryberry, T. Peterson.
%Improving computational efficiency in identifying parsimonious statistical models
%\textit{Idaho Conference on Undergraduate Research}. Boise, ID, July 2017.
%
%G. Cochrane, J. Edwards, D. Delparte.
%LiDAR Odometry and Mapping for Terrain Analysis from Unmanned Aerial Vehicles
%\textit{Idaho Conference on Undergraduate Research}. Boise, ID, July 2017.
%
%G. Cochrane, M. Sterbentz, J. Edwards.
%Real-Time LiDAR Terrain Mapping and Analysis
%\textit{Idaho Conference on Undergraduate Research}. Boise, ID, July 2016.
%
%J. Glines, J. Edwards.
%Isosurface Extyraction in a Simple C/C++ Library
%\textit{Idaho Conference on Undergraduate Research}. Boise, ID, July 2016.
%
%N. Vollmer, N. Harrison, J. Edwards.
%An Adaptive, Parallel Algorithm for Approximating the Generalized Voronoi Diagram
%\textit{Idaho Conference on Undergraduate Research}. Boise, ID, July 2016.
%
%J. Edwards, C. Johnson.
%Visualizing white matter tracts in the human brain.
%\textit{SIAM Conference on Computational Science and Engineering}. Salt Lake City, UT, March 2015.
%
%S. Kumar, B. Summa, C. Christensen, J. Edwards, V. Pascucci.
%Multi-resolution I/O for Massive Simulations: Enabling Scalable Visualization and Processing.
%\textit{Predictive Science Academic Alliance Program (PSAAP) TST Meeting}. Palo Alto, CA, May 2014.
%
%J. Edwards, E. Daniel, C. Bajaj, J. Kinney, T. Bartol, T. Sejnowski, K. Harris, D. Johnston.
%VolumeRoverN: Analysis-ready domain models of neuronal forests.
%\textit{2nd Annual Austin Translational Neuroscience Symposium}. Austin, TX, October 2012. \\
%$\star$ Best poster award
%
%%J. Edwards, J. Kinney, K. Harris, C. Bajaj. 
%%High quality 3D geometric models of hippocampal neuropil for electrophysiological simulation. 
%%\textit{Janelia Farm Conference on Large-Scale 3D Image Annotation, Management, and Visualization}. Ashburn, VA, October 2012.
%
%J. Edwards, A. Rand, J. Kinney, K. Harris, C. Bajaj. 
%Analysis-ready meshes of neuronal forests. 
%\textit{1st IEEE Symposium on Biological Data Visualization}. Providence, RI, October 2011.
%
%J. Edwards, A. Gillette, R. K. Bettadapura, A. Rand, C. Rumsey, Q. Zhang, D. Johnston, K. Harris, C. Bajaj. 
%Electrophysiological Models Derived from EM Reconstructions. 
%\textit{The National Academies Keck Futures Initiative Conference on Imaging Science}. November 2010.
%
%A. Gillette, R. K. Bettadapura, F. Chowdury, J. Edwards, A. Gopinath, J. Rivera, B. Subramanian, A. Rand, C. Rumsey, Q. Zhang, D. Johnston, K. Harris, C. Bajaj, T. Bartol, D. Keller, J. Kinney, T. Sejnowski. 
%Spatially Realistic and Reduced Electrophysiology Models Derived From EM Reconstruction. 
%\textit{MPG-HHMI Janelia Farm High-Resolution Circuit Reconstruction Conference}. Berlin, Germany, September 2009.
%
%
%\section{\sc Contributed talks}
%Separation of syntax and problem solving in Introductory Computer Programming.
%\textit{IEEE Frontiers in Education}. San Jose, CA. Oct 5, 2018.
%
%MagPhyx: simulation and visualization of magnet dynamics.
%\textit{Idaho Academy of Science and Engineering}. Pocatello, ID. April 1, 2016.
%
%Surface segmentation for improved isotropic remeshing.
%\textit{21st International Meshing Roundtable}. San Jose, CA. Oct 9, 2012.
%
%Topologically correct reconstruction of tortuous contour forests.
%\textit{14th ACM Symposium on Solid and Physical Modeling}. Haifa, Israel. September 1, 2010.
%
%Advanced techniques for LiDAR visualization and analysis using ArcGIS.
%\textit{8th International Lidar Mapping Forum}. Denver, CO. February 2008.
%
%%\newpage
%
%\section{\sc Invited talks}
%EdwardsLab: Visualization, geometry, and simulation.
%\textit{Will Pearse Biological Programming Group, Utah State University}. Logan, UT. Sept 28, 2018.
%
%The shape of thought: nanoscale geometry of hippocampal brain neurons.
%\textit{Geometric and Image Data Sciences: Big Data Analysis, Graphics and Visualization}. Austin, Texas. September 14, 2018.
%
%Geometric nanoscale modeling of neurons in 3D
%\textit{NeuroNex Workshop}. Austin, Texas. July 31, 2018.
%
%At the whiteboard: collaborative data science projects.
%\textit{Utah State University}. Logan, UT. Dec 8, 2017.
%
%Geometry and Topology: Brains, Bunnies, and Jet Engine Analysis.
%\textit{Graphics Seminar, The University of Texas}. Austin, TX. Feb 6, 2015.
%
%The adventure of discovery: geometry, topology and visualization.
%\textit{Idaho State University}. Pocatello, ID. Oct 17, 2014.
%
%Exploration of high-dimensional scalar functions.
%\textit{Computational Visualization Center group meeting}. Austin, TX. Nov 13, 2013.
%
%Analysis-ready models of tortuous, tightly packed geometries.
%\textit{University of Colorado Medical Center}. Denver, CO. Mar 1, 2013.
%
%Analysis-ready models of tortuous, tightly packed geometries.
%\textit{New Mexico State University}. Las Cruces, NM. Feb 15, 2013.
%
%Analysis-ready models of tortuous, tightly packed geometries.
%\textit{Scientific Computing and Imaging Institute}. Salt Lake City,
%UT. Feb 8, 2013.
%
%Cool Geometry Stuff.
%\textit{Leander High School, Anna Bouboulis Geometry Class}. Leander, TX. Jan 5, 2012.
%
%Surface segmentation for improved isotropic remeshing.
%\textit{University of Hong Kong graphics group meeting}. Hong Kong. May 30, 2012.
%
%Polyhedron separation.
%\textit{Computational Visualization Center group meeting}. Austin, TX. Sept 7, 2011.
%
%Analysis-ready 3D reconstructions of complex objects from planar cross-sectional slices.
%\textit{Computational Visualization Center group meeting}. Austin, TX. Mar 25, 2011.
%
%The connectome: challenges and approaches.
%\textit{Computational Visualization Center group meeting}. Austin, TX, Oct 27, 2010.
%
%LidarExplorer
%\textit{Advanced LiDAR Workshop at the GeoTREE Center of the University of Northern Iowa}. August 2007.
%
%%\section{\sc Other talks}
%%Analysis-ready models of tortuous, tightly packed geometries.
%%\textit{Thesis Defense}. Austin, TX, May 20, 2013.
%%
%%Analysis-ready domain models of neuronal forests.
%%\textit{Thesis proposal}. Austin, TX, Dec 13, 2011.
%%
%%Analysis-ready 3D reconstructions of complex objects from planar cross-sectional slices.
%%\textit{Research Preparation Exam}. Austin, TX, March 29, 2011.
%
%%\newpage
%
%\end{LONG}
%
%\section{\sc Conferences}
%\textit{ACM Special Interest Group for Computer Science Education (SIGCSE).} Portland, OR. March 2020.
%
%\textit{IEEE VIS.} Vancouver, BC. October 2019.
%
%\textit{ACM SIGGRAPH.} Los Angeles, CA. July 2019.
%
%\textit{NSF NeuroNex Workshop.} Austin, TX. June 2019.
%
%\textit{ACM Special Interest Group for Computer Science Education (SIGCSE).} Minneapolis, MN. February 2019.
%
%\textit{IEEE Frontiers in Education.} San Jose, California. October 2018.
%
%\textit{ACM Special Interest Group for Computer Science Education (SIGCSE).} Baltimore, MD. February 2018.
%
%\textit{Shape Modeling International.} Berkeley, CA. June 2017.
%
%\textit{Idaho EPSCoR Annual Meeting.} Coeur d'Alene, ID. October 2016.
%
%\textit{Idaho Conference on Undergraduate Research.} Boise, ID. July 2016.
%
%\textit{Idaho Academy of Science and Engineering}. Pocatello, ID. April 2016.
%
%\textit{Eurographics.} Zurich, Switzerland. July 2015.
%
%\textit{High Performance Computing, Networking, Storage and Analysis (SC14).} New Orleans, LA. November 2014.
%
%\textit{{IEEE VIS}.} Atlanta, GA. October 2013.
%
%\textit{21st International Meshing Roundtable.} San Jose, CA. October 2012.
%
%\textit{Austin Translational Neuroscience Symposium.} Austin, TX. October 2012.
%
%\textit{IEEE Symposium on Biological Data Visualization.} Providence, RI. October 2011.
%
%\textit{ACM Symposium on Solid and Physical Modeling.} Haifa, Israel. September 2010.
%
%\section{\sc Workshops}
%
%\textit{NSF Interactive Discussion: Computer Science Undergraduate Education in 2026 and Beyond.} SIGCSE. March 2, 2019.
%% Stephanie August (NSF)
%
%\textit{Planning and Writing Successful Grant Proposals.} Utah State University. Oct 15, 2018.
%
%\textit{Developing an Effective Propagation Plan for Educational Innovations.} IEEE FIE. Oct 5, 2018.
%
%\textit{How To Prepare Competitive NSF Engineering Education Proposals.} IEEE FIE. Oct 3, 2018.
%
%\textit{Geometric and Image Data Sciences: Big Data Analysis, Graphics and Visualization.} Austin, Texas. September 14, 2018.
%
%\textit{NSF NeuroNex 3DEM Workshop.} Austin, Texas. July 30-31, 2018.
%
%\textit{NSF Developing Empirical Education Research Studies (DEERS).} Charlottesville, VA. July 17-19, 2018.
%
%\textit{Deep Learning in the Classroom.} SIGCSE. February 23, 2018.
%% Doug Blank (Bryn Mawr), Lisa Meeden (Swarthmore), Jim Marshall (Sarah Lawrence)
%
%\textit{Designing Empirical Education Research Studies (DEERS): Creating an Answerable Research Question.} SIGCSE. February 21, 2018.
%% Mark Sherriff (U. of Virginia)
%
%\textit{Integrating Cloud Computing into the Computer Science Curriculum.} SIGCSE. February 21, 2018.
%% Laurie White (Google)
%
%\textit{NSF XSEDE Workshop on data modeling.} Boise State University. July 18-20, 2016.
%
%\textit{NIH BRAIN Initiative Summer Course on interdisciplinary computational neuroscience.} University of Missouri. June 5-17, 2016.
%
%\textit{Grant Writers Workshop.} Idaho State University. February 29, 2016.
%
%\textit{Promotion and Tenure Workshop.} Idaho State University. November 18, 2015.
%
%\textit{Interactive Cooperative Grant Training.} Idaho State University. August 31, 2015.
%
%\textit{Advanced LiDAR Workshop}. University of Northern Iowa. August 2007.
%
%\section{\sc Awards}
\section{\sc Honors}
\begin{itemize}[label={},leftmargin=0pt]
  \setlength\itemsep{0em}
  \item Teacher of the Year, USU CS Department, 2021
  \item Undergraduate Research Mentor of the Year, USU CS Department, 2020
  \item Translational Neuroscience Symposium Best Poster Award, 2012 %(\$200)
  \item The University of Texas, Computer Science PhD Fellowship, 2009 %(\$1000)
  \item Graduation \emph{Magna Cum Laude}, Utah State University, 1998
  \item Member \emph{Phi Kappa Phi} Honor Society, 1998
  \item Wendell Pope Scholarship, Utah State University, 1998
  \item Superior Student Scholarship, Utah State University, 1996-1998
\end{itemize}

\begin{LONG}
%\newpage
\end{LONG}

\section{\sc Professional service}
Program committee
\vspace{2mm}
\begin{itemize}[label={},leftmargin=5mm]
  \item IEEE Intermountain Engineering, Technology, and Computing (i-ETC) 2020
  \item International Conference on Geometric Modeling and Processing (GMP) 2015, 2016, 2017, 2018
\end{itemize}

Reviewer
\vspace{2mm}
\begin{itemize}[label={},leftmargin=5mm]
  \item National Goldwater Scholarship 2023
\end{itemize}

Reviewer
\vspace{2mm}
\begin{itemize}[label={},leftmargin=5mm]
  \item Journal of Educational Data Mining 2022
  \item Computer Science Education 2022, 2023
  \item ACM ITiCSE 2023
  \item ACM SIGCSE 2019, 2020, 2021, 2022, 2023
  \item Computer Animation and Virtual Worlds
  \item IEEE FIE 2018
  \item ACM Transactions on Mathematical Software, 2018
  \item GMP 2015, 2016, 2017, 2018
  \item Computing Surveys
  \item Computer Aided Geometric Design
  \item European Symposium on Algorithms 2014
  \item International Meshing Roundtable 2015
  \item SIGGRAPH Asia 2015
\end{itemize}

\section{\sc University service}
%\vspace{2mm}
\begin{itemize}[label={},leftmargin=0mm]
  \setlength\itemsep{0em}
  \item Member of Computer Science Undergraduate Curriculum Committee 2018-2020
  \item Member of Computer Science Faculty Search Committee 2019-2020
  \item Chair of CS faculty search committee 2017-2018 (ISU)
  \item University Research Council 2016-2018 (ISU)
  \item Health Informatics search committee 2016 (ISU)
  \item Author of CS Masters Degree proposal submitted 2018 (ISU)
\end{itemize}

\begin{LONG}

\section{\sc Expert witness}
\textit{State of Idaho v. Gabriel L. Moreno and Anthony C. Moreno}, 2018 \\
Case Nos. CR-2017-8408-FE and CR-2017-8409-FE, District Court, County of Bannock, Idaho \\
Nature of Case: Second degree murder.
\par \hangindent=0.7cm \parindent=0.7cm \parskip=0.0cm Plaintiff alleged malice aforethought in a fistfight resulting in a death. The defendant claimed self-defense. The event was captured on video and posted to Snapchat, which became the primary exhibit. I testified regarding the source and analysis of the video.\\

\parindent=0.0cm \textit{Employment-based immigration petition opinion letters}, 2018-current \\
Maystar, LLC
\par \hangindent=0.7cm \parindent=0.7cm \parskip=0.0cm Review immigration petitions of foreign employees in software engineering positions and provide opinion letters as to the educational requirements for their positions.

\section{\sc Other}
\parindent=0.0cm \textit{Interviewed in Deseret News article}, 2023\\
Title: \textit{How these Utah professors are addressing ChatGPT in the classroom}\\
https://www.deseret.com/2023/6/5/23688236/chatgpt-ai-college-classes-utah-professors-universities

%%\section{\sc Teaching}
%\section{\sc Courses taught}
%
%%Courses taught
%%\vspace{2mm}
%%\begin{itemize}[label={},leftmargin=5mm]
%\begin{itemize}[label={},leftmargin=0mm]
%  \setlength\itemsep{0em}
%%  \item CS 6150 Advanced Algorithms (with Valerio Pascucci, Fall 2013)
%%  \item CS 354 Computer Graphics (Spring 2013)
%%  \item CS 354 Computer Graphics (Fall 2012)
%%  \item CS 108 UNIX (Fall 2011)
%%  \item CS 105 C++ (Spring 2011)
%%  \item CS 105 C++ (Fall 2010)
%  \item Data Science Incubator
%  \item Data Visualization
%  \item Graduate Algorithms
%  \item Computer Graphics
%  \item Compilers
%  \item Operating Systems
%  \item Algorithms and Data Structures
%  \item Introductory Programming
%\end{itemize}
%
%%Teaching assistant
%%\vspace{2mm}
%%\begin{itemize}[label={},leftmargin=5mm]
%%  \setlength\itemsep{0em}
%%  \item CS 312 Introduction to Programming (Summer 2012)
%%  \item CS 354 Computer Graphics (Spring 2010)
%%  \item CS 303E Elements of Programming (Fall 2009)
%%\end{itemize}

%\section{\sc Students}
%\begin{itemize}[label={},leftmargin=0pt]
%  \setlength\itemsep{0em}
%  \item Joseph Ditton (Masters)
%  \item Daniel Marsden (Masters)
%  \item Bishal Sainju (Masters)
%  \item Chetan Birthare (Masters)
%  \item Mason Pachner (Masters)
%  \item Steven Scott (Undergraduate)
%  \item Bo Johnson (Undergraduate)
%\end{itemize}
%
%\section{\sc Past students}
%\begin{itemize}[label={},leftmargin=0pt]
%  \setlength\itemsep{0em}
%  \item Joseph Valentin (Undergraduate, Idaho State University)
%  \item John Motley (Undergraduate, Idaho State University)
%  \item Galen Cochrane (Undergraduate, Idaho State University)
%  \item Jacqueline Ory (Undergraduate, now at IRI)
%  \item Nathan Morrical (Undergraduate, now PhD student at University of Utah)
%  \item Marko Sterbentz (Undergraduate, now Masters student at University of Southern California)
%  \item Jonathan Glines (Undergraduate, now at NVIDIA)
%  \item Nicholas Harrison (Undergraduate, now at Clearwater, Inc.)
%  \item Zackary Hall (Undergraduate, now at Clearwater, Inc.)
%%  \item Zinnia Mukherjee (Masters, University of Utah)
%%  \item Sidharth Kumar (Postdoc, University of Utah)
%%  \item Laura Lediaev (PhD, University of Utah)
%%  \item Eric Greg Daniel (Google)
%\end{itemize}
%
%\section{\sc Collaborations}
%Computer Science
%\vspace{2mm}
%\begin{itemize}[label={},leftmargin=5mm]
%  \setlength\itemsep{0em}
%  \item Arto Hellas (University of Helsinki)
%  \item Juho Leinonen (University of Helsinki)
%  \item Paul Bodily (Idaho State University)
%  \item Isaac Griffith (Idaho State University)
%  \item Kevin Parker (Idaho State University)
%  \item Jonathan Holmes (Idaho State University)
%  \item Valerio Pascucci (SCI, University of Utah)
%  \item Christopher Johnson (SCI, University of Utah)
%  \item Chandrajit Bajaj (University of Texas)
%  \item Wenping Wang (University of Hong Kong)
%  \item Peer-Timo Bremer (Lawrence Livermore National Laboratories)
%  \item Attila Gyulassy (SCI)
%  \item Brian Summa (SCI, University of Utah)
%  \item Josh Johnston (Boise State University)
%  \item Parris Egbert (Brigham Young University)
%\end{itemize}
%
%\vspace{2mm}
%Other disciplines
%\vspace{2mm}
%\begin{itemize}[label={},leftmargin=5mm]
%  \setlength\itemsep{0em}
%  \item Chris Hartwell (Business, Utah State University)
%  \item Tracy Payne (Mathematics, Idaho State University)
%  \item DeWayne Derryberry (Statistics, Idaho State University)
%  \item Teri Peterson (Statistics, Idaho State University)
%  \item Ken Aho (Biology, Idaho State University)
%  \item Justin Stover (History, Idaho State University)
%  \item Steven Shropshire (Physics, Idaho State University)
%  \item Boyd Edwards (Physics, Utah State University)
%  \item Donna Delparte (Geosciences, Idaho State University)
%  \item Andrew Gillette (Mathematics, University of Arizona)
%  \item Terrence Sejnowski (Neuroscience, Salk Institute)
%  \item Tom Bartol (Neuroscience, Salk Institute)
%  \item Kristen Harris (Neuroscience, University of Texas)
%  \item Justin Kinney (Neuroscience, Massachussetts Institute of Technology)
%  \item Daniel Johnston (Neuroscience, University of Texas)
%\end{itemize}

\end{LONG}

\end{resume}
\end{document}

