%%%%%%%%% BIOGRAPHICAL SKETCH -- 2 pages

\documentclass[svgnames,12pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage[T1]{fontenc}
\usepackage{times}
\usepackage{url}
\usepackage{booktabs}
\renewcommand\thesection{(\alph{section})}
\renewcommand\thesubsection{(\alph{subsection})}

\newenvironment{tightenumerate}{
\begin{enumerate}
  \setlength{\itemsep}{1pt}
  \setlength{\parskip}{0pt}
  \setlength{\parsep}{0pt}
}{\end{enumerate}
}
\newenvironment{tightitemize}{
\begin{itemize}
  \setlength{\itemsep}{1pt}
  \setlength{\parskip}{0pt}
  \setlength{\parsep}{0pt}
}{\end{itemize}
}

\begin{document}

\begin{center}
\begin{large}\textbf{Biographical Sketch} \\
John M. Edwards, Assistant Professor \\ \end{large}
Idaho State University \\
edwajohn@isu.edu \\
%(208) 282-4876 \\
\end{center}

%\textbf{(a) Professional Preparation} \\
\subsection*{Professional Preparation}
\begin{tabular}{llll}
Institution & Location & Major & Degree, Year \\
\midrule
Utah State University & Logan, Utah & Computer Science & B.S., 1998 \\
Brigham Young University & Provo, Utah & Computer Science & M.S., 2004 \\
The University of Texas & Austin, Texas & Computer Science & Ph.D., 2013 \\
The University of Utah & Salt Lake City, Utah & Visualization & Postdoc, 2013-2015
\end{tabular}

\subsection*{Appointments}
\begin{tabular}{lll}
Period & Appointment & Institution \& location \\
\midrule
2015-Present & Assistant Professor & Idaho State University, Pocatello, ID \\
2012 & Visiting Scholar & University of Hong Kong, Hong Kong, China \\
%2010-2013 & Assistant Instructor & The University of Texas \\
2008-2009 & Visualization Research Engineer & Autonomous Solutions, Inc., Logan, UT \\
2005-2008 & Software Engineer & ProLogic, Inc., Fairmont, WV \\
1999-2005 & Software Engineer & Rigaku, Inc., Houston, TX
\end{tabular}

\subsection*{Products}
\paragraph{Selected Publications}
\begin{tightenumerate}
\item Xin Tong, John Edwards, Chun-Ming Chen, Han-Wei Shen, Christopher Johnson, and Pak Chung Wong. View-dependent streamline deformation and exploration. \textit{IEEE Transactions on Visualization and Computer Graphics}. 22(7):1788-1801. 2016.
%\item Xin Tong, John Edwards, Chun-Ming Chen, Han-Wei Shen, Christopher Johnson, and Pak Chung Wong. View-dependent streamline deformation and exploration. \textit{IEEE Transactions on Visualization and Computer Graphics}. \textit{accepted for publication}. 2015.
\item John Edwards, Eric Daniel, Valerio Pascucci, Chandrajit Bajaj. Approximating the Generalized Voronoi Diagram of Closely Spaced Objects. \textit{Computer Graphics Forum}. 34(2):299-309. 2015.
\item John Edwards, Eric Daniel, Justin Kinney, Terrence Sejnowski, Tom Bartol, Daniel Johnston, Kristen Harris, and Chandrajit Bajaj. VolRoverN: Enhancing surface and volumetric reconstruction for realistic dynamical simulation of cellular and subcellular function.  \textit{Neuroinformatics}. 12(2):277-289.  2014.
\item Sidharth Kumar, John Edwards, Peer-Timo Bremer, Aaron Knoll, Cameron Christensen, Venkatram Vishwanath, Philip Carns, John A. Schmidt, Valerio Pascucci. Efficient I/O and storage of adaptive resolution data. \textit{High Performance Computing, Networking, Storage and Analysis (SC14)}. New Orleans, LA, November 2014.
% 21\% acceptance rate
\item John Edwards and Chandrajit Bajaj. Topologically correct reconstruction of tortuous contour forests. \textit{Computer-Aided Design}. 43(10):1296-1306. 2011.
\end{tightenumerate}

\newpage

\paragraph{Additional Publications and Research Software}
\begin{tightenumerate}
\item Boyd Edwards and John Edwards. Dynamical interactions between two uniformly magnetized spheres. European Journal of Physics, 38(1):015205, 2016.
\item John Edwards, Sidharth Kumar, and Valerio Pascucci. Big data from scientific simulations. In L. Grandinetti, G.R. Joubert, M. Kunze, and V. Pascucci, editors, \textit{Big Data and High Performance Computing}, pages 32--46. IOS Press, Amsterdam, Berlin, Tokyo, Washington, DC, 2015.
\item John Edwards, Wenping Wang, and Chandrajit Bajaj. Surface segmentation for improved remeshing. \textit{Proceedings of the 21st International Meshing Roundtable}, pages 403-418. San Jose, CA, October 2012.
\item \emph{MagPhyx} - Magnet simulation software\\
\url{http://www2.cose.isu.edu/~edwajohn/MagPhyx}
\item \emph{VolRoverN} - Neuronal reconstruction and geometric analysis\\
\url{http://www.cs.utexas.edu/~bajaj/cvcwp/?page_id=2089}
%\url{http://www.cs.utexas.edu/$\sim$bajaj/cvcwp/?page\_id=2089}
\end{tightenumerate}

\subsection*{Synergistic Activities}
\begin{tightenumerate}
\item \textbf{Program committee:} International Conference on Geometric Modeling and Processing (GMP) 2015, 2016, 2017, 2018. \textbf{Reviewer:} GMP 2015, 2016, 2017, Computing Surveys, Computer Aided Geometric Design, European Symposium on Algorithms 2014, International Meshing Roundtable, SIGGRAPH Asia 2015. \textbf{Session chair:} Idaho Academy of Science and Engineering Annual Meeting, 2016.
\item \textbf{Neuroscience:} Attended competitive NIH BRAIN Initiative Summer Course on interdisciplinary computational neuroscience, July 2016.
%\item \textbf{Geoscience:} Contributor in Managing Idaho's Landscapes for Ecosystem Services (MILES), an NSF-funded project to understand social and ecological systems.
\item \textbf{Outreach:} Acted as faculty advisor to student-led Google igniteCS high school outreach workshop series to Blackfoot High School, Spring 2017. Faculty advisor to Google ig- niteCS/Idaho STEM Action Center middle school outreach workshop series to eight local middle schools, Fall 2017.
\item \textbf{Teaching:} Development and delivery of undergraduate courses on graphics, compilers, operating systems; graduate course on advanced algorithms. 2013-2016. Teaching Innovation Grant for Introductory Computer Programming course, 2017.
\item \textbf{Advising:} Selected undergraduate students advised in research projects: Nathan Morrical (now at UofU) - Parallel GVD; Marko Sterbentz (now at USC) and Galen Cochrane - Lidar data collection and analysis; Jonathan Glines (now at NVIDIA) - Bird flocking analysis.
%\item \textbf{NSF EPSCoR MILES mentor:} - supervised three students over two years to develop cutting edge Lidar collection, visualization and analysis software. (Award No. IIA-1301792)
\end{tightenumerate}

\end{document}
